Hybrid platforms and bargaining power

### 2023-04-10 src/paper/application.tex
Add abstract

\begin{abstract}
\end{abstract}

>>>>

\begin{abstract}
    This paper studies the effects of a platform selling their own products in addition to acting as intermediaries (hybrid platforms) in a setting when bargaining takes place between the platform and the potential entrants.
    It highlights a so-far underexplored aspect of hybrid platforms: having their own products increases their bargaining power over the other sellers.
    As shown through a more concrete example, this change in bargaining power can have negative welfare consequences for the consumers.
    The results and methods described in this paper are also applicable to other similar settings, such as vertical integration with a monopolistic upstream supplier.
\end{abstract}
